Road Segment Prioritization for Bicycle Infrastructure

### 2021-01-04 README.Rmd
minor typos + added README inside R directory with reproducibility instructions

The approach is based on origin-destination (OD), which can be obtained from many sources.
In this paper we use open access data from the UK census [@ONS2011flowdata], which contains aggregate statistics on number of commuters between Middle layer Super Output Area (MSOA) zones, which have an average just over 8000 [@ofn2018population].

@@

This paper provides a methodology for prioritizing road segments for investments in cycling infrastructure, with the output being a proposed cycling network for the city under study. 
The approach aims to respect both the needs of the users and the ambitions of stakeholders working at local/regional levels.
The results, primarily detailed route network maps based on current travel behaviour derived from origin-destination data, can starting point for introducing a direct, connected, and low-stress network for any city by leveraging available open data. The only data necessary for reproducing it is the road network (from OSM), its topography (from satellite imagery), and commuter data (from the national census)^[The results are easily reproducible for all UK cities, and can also be reproduced for cities elsewhere given the availability of commuter data. Instructions for reproducing the results are detailed in this [Github repository](https://github.com/Hussein-Mahfouz/cycle-networks)].

The approach is not without limitations.
The level of detail is only as good as the granularity of the available data (in this case relatively coarse zones).
@iacono2010measuring note that such large travel zones are not ideal for understanding route choice behaviour of cyclists and pedestrians. They also give rise to an \`ecological fallacy' whereby average characteristics are assumed to apply to all residents of the aggregated geographical area, suggesting a need to applying the methods to more granular origin-destination data (and for governments and other data-collecting organisations to make origin-destination more readily available).

>>>>

The approach is based on origin-destination (OD), which can be obtained from many sources.
In this paper we use open access data from the UK census [@ONS2011flowdata], which contains aggregate statistics on number of commuters between Middle layer Super Output Area (MSOA) zones, which have an average population of just over 8000 [@ofn2018population].

@@

This paper provides a methodology for prioritizing road segments for investments in cycling infrastructure, with the output being a proposed cycling network for the city under study. 
The approach aims to respect both the needs of the users and the ambitions of stakeholders working at local/regional levels.
The results, primarily detailed route network maps based on current travel behaviour derived from origin-destination data, can be a starting point for introducing a direct, connected, and low-stress network for any city by leveraging available open data. The only data necessary for reproducing it is the road network (from OSM), its topography (from satellite imagery), and commuter data (from the national census)^[The results are easily reproducible for all UK cities, and can also be reproduced for cities elsewhere given the availability of commuter data. Instructions for reproducing the results are detailed in this [Github repository](https://github.com/Hussein-Mahfouz/cycle-networks)].

The approach is not without limitations.
The level of detail is only as good as the granularity of the available data (in this case relatively coarse zones).
@iacono2010measuring note that such large travel zones are not ideal for understanding route choice behaviour of cyclists and pedestrians. They also give rise to an \`ecological fallacy' whereby average characteristics are assumed to apply to all residents of the aggregated geographical area, suggesting a need for applying the methods to more granular origin-destination data (and for governments and other data-collecting organisations to make origin-destination data more readily available).
